---
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# GazetteR
  
The purpose of this package is to facilitate the easy analysis of The Gazette information in R.  

It achieves this by enabling users to search the online Gazette and identify notices that they are interested in obtaining.  It then obtains those notices and allows users to search the notice content to establish if they are relevant. All this data is then available in R dataframes to facilitate further analysis such as text analysis or linking to other datasets such as OpenStreetMap or Official National Statistics.   
   
   
### The Gazette - the Official Public Record in the UK

The Gazette is the Official Public Record combining three publications: The London Gazette, The Belfast Gazette and The Edinburgh Gazette. It predominantly consists of statutory notices i.e. where a person or organisation or company is legally required to advertise an event or proposal in The Gazette. Notices can only be placed in The Gazette by: registered and verified people, who are acting in an official capacity and who have the authority to create an official record of fact e.g. solicitors, executers of will.       

It contains over 450 different types of notices. Key categories include:

- Public notices - these are placed by local authorities, government agencies or public bodies when there is a legal requirement or they are in the public interest.  These include transport and highways notices, planning applications, and notices relating to health, agriculture, environment and infrastructure, including public services. 

- State notices - state and parliamentary notices placed by the Crown and some government organisations. 

- Other public sector notices - ecclesiastical, public finance and unclaimed estate notices.

- Insolvency notices - corporate and private insolvency notices.

- Personal legal - notices that individuals or legal professionals may need to make publicly available e.g. changes or name, deceased estates 

- Other notices - contains all other notices that do not fall into the above categories e.g. companies regulation, partnerships and societies regulation

Information on the different types of notices can be found here <https://www.thegazette.co.uk/noticecodes>.

The Gazette also publishes specific supplements that gather together certain notices in a special edition. These include the Company Law Supplement containing details of information notified to or by Companies House such as Certificates of incorporation, company's memorandum and articles, company's directors etc; and the Ministry of Defence Supplement.    
  
  
The Gazette provides an online search function to identify notices.  This search facility includes the ability to search by:

- free text

- notice type (1998 onwards) 

- notice code 

- location(s) - postcode or place with a certain number of miles OR local authority (drop-down list)

- publication dates

- Gazette edition (London, Edinburgh or Belfast)

The search facility returns a page of notices (defaulting to 10) displaying the Publication Date, a title (wording depends on search approach used but may be notice category, legal act etc), the first few lines of the notice content and a link to viewing the full notice. Links to additional pages of results are displayed at the bottom of the page aswell as the total number of search results.  

The Gazette has developed a API interface that allows authorised people to place notices but also allows other users to view Gazette content.  
Details on the Data formats can be found here <https://www.thegazette.co.uk/data/formats>.
The Developer Documentation for this interface is available at: <https://github.com/TheGazette/DevDocs/blob/master/home.md>

### GazetteR installation

You can install the developed version of CycleInfraLnd from [Github](https://github.com/PublicHealthDataGeek/GazetteR) with:

``` r
install.packages("devtools")
devtools::install_github("PublicHealthDataGeek/GazetteR")
```
Please note that The Gazette requests that users perform activity in non-business hours i.e. between 9pm and 7am. 

### GazetteR functions

These examples show how to get data from The Gazette Search and return it in a tidied or non-tided format. 

```{r example}
library(GazetteR)
test_tidy = get_gazette_feed(
  categorycode = 15,
  start_publish_date = "01/01/2021",
  end_publish_date = "31/01/2021"
) # returns tidied data with column headings that make sense and dates in correct date format
names(test_tidy)

test_non_tidy = get_gazette_feed(
  categorycode = 15,
  start_publish_date = "01/01/2021",
  end_publish_date = "31/01/2021",
  tidy = FALSE
) # return non-tidied data with original column headings and all data as character data type
names(test_non_tidy)

```
  
Other functions allow you to get more data including the full text content of the notice. For example, `get_notice_content` allows you to specify a particular notice and extract more data such as the full text content of the notice and the borough.  This function also lets you search the content and returns a TRUE/FALSE column depending on whether that terms is found in the content. 
```{r}
# From URL: https://www.thegazette.co.uk/notice/3487301
content_3725064 = get_notice_content(3725064, "contraflow")
names(content_3725064)
```

```{r, echo = FALSE}
content_3725064[, 1:5] %>%
  knitr::kable()
```

```{r, echo = FALSE}
content_3725064[, 6:8] %>%
  knitr::kable() %>%
  kableExtra::column_spec(1, width = "50em") %>%
  kableExtra::column_spec(2, extra_css = "vertical-align:top") %>%
  kableExtra::column_spec(3, extra_css = "vertical-align:top")
```
  
You can then join this data to the results of the `get_gazette_feed`.  

```{r}
notice_3725064 = dplyr::left_join(content_3725064, test_tidy, by = "notice_id")
names(notice_3725064)
```
  
The final function, `get_content` allows you to get the notice content for a list of notices. 

```{r}
content = get_content(c(3725064, 3487301), search_terms = "contraflow")
dim(content)
```


### The Gazette and GazetteR limitations
The GazetteR package reflects the limitations of The Gazette API and website.  For example, The Gazette API states is it possible to use both categorycode and noticetype as parameters (categorycode being higher level e.g. 15 for transport whilst noticetype is subcategories eg 1501 for Road Traffic Acts).  However, we have not managed to get noticetype to work so have had to stick with categorycode. NB Confusing the API uses the terms categorycode and noticetype but The Gazette website search facility calls these 'Notice type' for categorycode and 'Notice code'' for noticetype.  

The data returned by the `get_gazette_feed` function reflects the limited content returned by The Gazette online search, namely a publication date, title and a few lines of content plus additional data such as the unique notice id, notice url and the 4 digit notice code from the API.  

This package was originally developed to look for notices that introduce contraflow bike lanes in London Boroughs specifically for notices with a category code of 15).  So some of the column headings may be inappropriate for other searches.  This package hasnt been tested with other Gazette category codes so the structure and content of the data returned may not be quite right. 

Please raise as issues or requests via the github issue page and I will get to these as an when I can.  If anyone is interested in collaborating to improve the code or make it more robust for other searches then please get in touch via ugm4cjt@leeds.ac.uk.  
